\documentclass[11pt,largemargins]{homework}

\newcommand{\hwname}{}
\newcommand{\hwemail}{arthurg}
\newcommand{\hwtype}{}
\newcommand{\hwnum}{}
\newcommand{\hwclass}{cs224n}
\newcommand{\hwlecture}{a5}
\newcommand{\hwsection}{}

% This is just used to generate filler content. You don't need it in an actual
% homework!
\usepackage{lipsum}

\begin{document}
\maketitle

\question

When using convolutions on character level language models, the convolutions (of size k) are able to operate on words of arbitrary length. However, the output of this convolution will be a vector of size $len - k$. 

\question

The minimum $w_{word}$ is 1. After padding the $sow$ and $eow$ tokens,  the minimum length for $x_{padded}$ would thus be $R^{1+2} = R^{3}$

To ensure we apply at least one full convolution, we need to padd $x_{padded}$ to size 5. Then, we need padding of 1. $x_{reshaped} \in R^{e_{char} x 1 + 2 + (2 * 1)} =  R^{e_{char} x 5}$

\question
It's useful for the extremes of $x_{gate}$ to set $x_{highway}$ be either fully $x_{proj}$ or fully $x_{conv\_out}$ because it allows certain character embeddings to optionally pass through another layer. 

It's probably a better idea to set the bias to positive. This will ensure $x_{gate} -> 1$. If $x_{gate} = 0$, we will have no gradient on $x_{proj}$ which makes the layer useless. 

\question

- Parallizes better on GPUs

- Multi-headed attention might improve translation accuracy when trying to do things like verb - noun agreements 

\question 

I tested my Highway network by:

1. Running a batch of $x_{conv\_out}$ to check the dimensions are correct 

2. Set the weights of $w$, and send in an $x_{conv\_out}$ vector (of size 5). Manually do the matrix math to check the output matches. In these test cases, I made sure to find cases where the sigmoid is 0, sigmoid is 1, and where the relu is 0. 

I'm confident that these two tests will cover the edge cases. In general, since I used pre-defined components in PyTorch, most of the edge cases are handled for me. 

\question 

I tested my CNN network by:

1. Running the CNN on a batch of $x_{emb}$ to check the dimensions are correct 

2. Set the weights of $w$, and send in an $x_{emb}$. Through hand computing the convlustion, and pooling operation, I manually network was acting properly. 

3. Set the weights of $w$, and send in an $x_{emb}$. Through hand computing the convlustion, and RELU operation, I manually network was acting properly. 

I'm confident that these three tests will cover the edge cases. In general, since I used pre-defined components in PyTorch, most of the edge cases are handled for me. 

\question 

My BLEU score is 36.51893424356271

\question 

traducir -> Not in vocab 

traduzco -> In vocab 

traduces -> Not in vocab 

traduce -> In vocab 

traduzca -> In vocab 
 
traduzcas -> Not in vocab 


This would be bad for the word-based NMT because the encoder would be unable to a few conjugations of 'traducir'. If the unseen versions of the verb occurs in the test set, the system likely output an <UNK> word. 

The character-based NMT model overcomes this as it would likely learn an embedding for the common substring, namely 'tradu'. Then, if it sees a conjugation of the verb that is not in the vocab, it uses the prefix of the word to estimate an embedding, and then this prefix will most likely accuratley encode the meaning. 

\question

Financial -> Economic

Neuron -> Nerve

Francisco -> San

naturally -> occuring 

expectation -> norms 

\question 


Financial -> Vertical

Neuron -> Newton

Francisco -> France 

naturally -> practically 

expectation -> exception 


\question

In the Word2Vec embeddings, it appears that the neighbours have similar meaning or are words that are used in conjunction with one another.

In the CharCNN embeddings, it appears that the neighbours have either a similar prefix or suffix. Most of the time, the neighbours don't have any relation to one another semantically. 

\question 
Incorrect example first 


Source: Hoy estoy aqu para hablarles sobre crculos y epifanas.

Reference : I'm here today to talk to you  about circles and epiphanies.
 
Output (A4): I'm here to talk to you about circles and <unk>
 
Output (A5): I'm here today to talk to you about circles and epidemiologists.


The UNK got translated as epidemiologists. 

During this translation, i think the encoder encountered 'epifanas' in spanish which it never saw before. So, it probably used the CharCNN model, which means that the word had similar embedding to 'epidemióloga' (meaning epiodemiologist). Then, the decoder probably had the word 'epidemiologist' in its vocab, and outputed that. 
 
Correct Example"

Source: Entonces ella me deca: "Bueno y qu hars cuando vengas?"   

Reference: And she'd say, "Well what are you going to do when you get here?

Output (A4) : So she said, "Well what are you going to do when you <unk>

Output (A5) : So she said,``Well, what do you do  when you come? ''

The UNK got translated as 'get here'

During this translation, I think the encoder encountered 'vengas', which was probably not in the spanish vocab for the encoder. As a result, in A4, this was translated as UNK. In a5, I believe the CharCNN model encoder was probably able to find a match for the root word of 'vengas' (perhaps venir?). Then, the word was decoded properly. 

\end{document}
